### 2014-02-27 src/paper.Rnw
remove R for now

<<a,message=F, echo=F>>=
require(xtable)
require(data.table)
load('data/mu.rda')
@

@@

<<prepare,echo=F>>=
attach(m)
sdl_f <- mut.avg~sdl.mut.avg + 0
rnd_f <- mut.avg~lrnd.mut.avg + 0

sdl_all <- lm(sdl_f)
rnd_all <- lm(rnd_f)

sdl_s <- summary(sdl_all)
rnd_s <- summary(rnd_all)

sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']

sdl.r <- sdl_s$r.squared
rnd.r <- rnd_s$r.squared

@

\begin{figure*}[t]
<<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
plot(sdl_f, main='SDL ~ ALL',pch='*')
abline(sdl_all, col='red')
plot(rnd_f, main='RND ~ ALL',pch='*')
abline(rnd_all, col='blue')
abline(sdl_all, col='red', lty=2)
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots of total mutation number, and those killed.}
\label{fig:caddrm}
\end{figure*}

@@

<<>>=
c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
@

$ \mu_\{M_{all} | M_{sdl}\} = \Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = \Sexpr{sdl.r} \text{,} \tau_{\beta} = \Sexpr{c}$

@@

$ \mu_\{M_{all} | M_{rnd}\} = \Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = \Sexpr{rnd.r} \text{,} \tau_{\beta} = \Sexpr{d}$

@@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of \Sexpr{s$p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,sdl.mut.avg))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
print(xtable(sm,caption="My caption"), size="\\small")
@
\end{small}

@@

\begin{figure*}[t]
<<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
t_f <- sdl.time~lrnd.time
plot(t_f, main='SDL ~ RND',pch='*')
abline(lm(t_f), col='red')
detach(m)
@
\caption{Time}
\label{fig:caddrm}
\end{figure*}

>>>>

% <<a,message=F, echo=F>>=
% require(xtable)
% require(data.table)
% load('data/mu.rda')
% @

@@

% <<prepare,echo=F>>=
% attach(m)
% sdl_f <- mut.avg~sdl.mut.avg + 0
% rnd_f <- mut.avg~lrnd.mut.avg + 0
% 
% sdl_all <- lm(sdl_f)
% rnd_all <- lm(rnd_f)
% 
% sdl_s <- summary(sdl_all)
% rnd_s <- summary(rnd_all)
% 
% sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
% rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
% 
% sdl.r <- sdl_s$r.squared
% rnd.r <- rnd_s$r.squared
% 
% @

\begin{figure*}[t]
% <<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% plot(sdl_f, main='SDL ~ ALL',pch='*')
% abline(sdl_all, col='red')
% plot(rnd_f, main='RND ~ ALL',pch='*')
% abline(rnd_all, col='blue')
% abline(sdl_all, col='red', lty=2)
% @
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
% <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
% hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% 
% hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
% hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% 
% hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
% hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% @
\caption{Plots of total mutation number, and those killed.}
\label{fig:caddrm}
\end{figure*}

@@

% <<>>=
% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
% @

$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$

@@

$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$

@@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
% <<results='asis'>>=
% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
% s$type <- 'sdl'
% colnames(s) <- c('mut', 'sample', 'type')
% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
% r$type <- 'rnd'
% colnames(r) <- c('mut', 'sample', 'type')
% all <- rbind(s, r)
% fm <- with(all, lm(mut ~ sample + type + sample:type))
% sm <- anova(fm)
% print(xtable(sm,caption="My caption"), size="\\small")
% @
\end{small}

@@

\begin{figure*}[t]
% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% t_f <- sdl.time~lrnd.time
% plot(t_f, main='SDL ~ RND',pch='*')
% abline(lm(t_f), col='red')
% detach(m)
% @
\caption{Time}
\label{fig:caddrm}
\end{figure*}
